---
title: "R/Pharma genAI Day 2026"
subtitle: "Information on R/Pharma's third genAI single day event"
title-block-banner: "#EDF3F9"
title-block-banner-color: body
page-layout: full
format:
  html:
    include-in-header:
      text: |
        <link rel="stylesheet" href="https://unpkg.com/tippy.js@6/themes/light.css">
        <script src="https://unpkg.com/@popperjs/core@2"></script>
        <script src="https://unpkg.com/tippy.js@6"></script>
        <link rel="stylesheet" href="schedule.css">
        <script src="schedule.js"></script>    
---

The third Annual R/Pharma genAI Day has wrapped up.  The single-day event featured examples of using generative and agentic artificial intelligence with an emphasis in the drug development space and clinical domain.  950 attendees participated.  Thank you to everyone who came and everyone who contributed.

Recordings are available on the [events](/docs/events) page.

```{r}
#| echo: FALSE
#| warning: FALSE
library(yaml)
library(purrr)
library(tibble)
library(htmltools)

file <- here::here("data", "schedule.yml")
raw <- yaml::read_yaml(file)

normalize_speakers <- function(s) {
  if (is.null(s)) return(NULL)
  lapply(s, function(x) {
    list(
      name = x$name,
      affiliation = if (!is.null(x$affiliation) && nzchar(x$affiliation)) x$affiliation else NULL,
      bio = x$bio %||% ""
    )
  })
}

default_track <- "us_europe"

schedule <- tibble(
  time = map_chr(raw, "time"),
  type = map_chr(raw, "type"),
  title = map_chr(raw, "title"),
  duration = map_chr(raw, "duration"),
  abstract = map_chr(raw, ~ .x$abstract %||% ""),
  speakers = map(raw, ~ normalize_speakers(.x$speakers)),
  track = map_chr(raw, "track" %||% default_track)
)

speaker_tag <- function(name, affiliation, bio) {

  has_text <- function(x) {
    !is.null(x) && length(x) == 1 && !is.na(x) && nzchar(x)
  }

  label <- name
  if (has_text(affiliation)) {
    label <- paste0(name, " (", affiliation, ")")
  }

  if (has_text(bio)) {
    tags$span(
      class = "has-tooltip speaker",
      `data-tippy-content` = paste0(
        "<strong>", name, "</strong>",
        if (has_text(affiliation)) {
          paste0("<br><em>", affiliation, "</em>")
        } else "",
        "<br><br>", bio
      ),
      HTML(label)
    )
  } else {
    tags$span(class = "speaker", label)
  }
}

speakers_block <- function(speakers) {

  if (is.null(speakers) || length(speakers) == 0) return(NULL)

  # 🔑 unwrap common YAML/list-column nesting issue
  if (length(speakers) == 1 && is.list(speakers[[1]]) && !is.null(speakers[[1]][[1]]$name)) {
    speakers <- speakers[[1]]
  }

  tagList(
    purrr::imap(speakers, function(sp, i) {
      tagList(
        speaker_tag(
          sp$name %||% "",
          sp$affiliation %||% "",
          sp$bio %||% NULL
        ),
        if (i < length(speakers)) ", "
      )
    })
  )
}

title_tag <- function(title, abstract) {

  has_text <- function(x) {
    !is.null(x) && length(x) == 1 && !is.na(x) && nzchar(x)
  }

  if (has_text(abstract)) {
    tags$span(
      class = "has-tooltip talk-title",
      `data-tippy-content` = paste0(
        "<strong>Abstract</strong><br><br>", abstract
      ),
      title
    )
  } else {
    tags$span(class = "talk-title", title)
  }
}

render_row <- function(row) {

  if (row$type == "break") {
    return(
      tags$div(class = "schedule-row break",
        tags$div(class = "time", row$time),
        tags$div(class = "content",
          tags$strong(row$title),
          tags$span(class = "duration", row$duration)
        )
      )
    )
  }

  tags$div(class = "schedule-row talk",
    tags$div(class = "time", row$time),
    tags$div(class = "content",

      speakers_block(row$speakers),

      if (!is.null(row$speakers) && length(row$speakers) > 0) tags$br(),

      tags$div(class = "title-row",
        title_tag(row$title, row$abstract),
        tags$span(class = "duration", row$duration)
      )
    )
  )
}

render_schedule <- function(df) {
  tags$div(
    class = "schedule-container",
    tagList(
      lapply(seq_len(nrow(df)), function(i) {
        render_row(df[i, ])
      })
    )
  )
}

```

## Europe/US Schedule

Tap or hover on talk titles for abstracts and speaker names for bios.  All times are in EDT on **June 16, 2026**.

```{r}
#| echo: FALSE
#| output: asis

schedule_us_europe <- dplyr::filter(schedule, track == "us_europe")
render_schedule(schedule_us_europe)
```


## APAC Schedule

R/Pharma is exited to bring the first APAC-targeted schedule this year.  
Tap or hover on talk titles for abstracts and speaker names for bios.  All times are in IST on **June 17, 2026**.

```{r}
#| echo: FALSE
#| output: asis

schedule_apac <- dplyr::filter(schedule, track == "apac")
render_schedule(schedule_apac)
```