---
title: "R/Pharma genAI Day 2026"
subtitle: "Information on R/Pharma's third genAI single day event"
title-block-banner: "#EDF3F9"
title-block-banner-color: body
page-layout: full
format:
  html:
    include-in-header:
      text: |
        <link rel="stylesheet" href="https://unpkg.com/tippy.js@6/themes/light.css">
        <script src="https://unpkg.com/@popperjs/core@2"></script>
        <script src="https://unpkg.com/tippy.js@6"></script>
        <link rel="stylesheet" href="schedule.css">
        <script src="schedule.js"></script>    
---

:::: {.hero-buttons-ai}
[genAI Day Registration](https://events.zoom.us/ev/AkKYQ7Uryr8k8HeuQ7F6rkZTHJwjHlP6gxu14Z2s1LYb0kswLdDT~ApU4J3CViJWrwmjZhnw0nwGzDFCxNGoMHJAw01NbG30yNwnVwf9IJQkvOg){.btn-action-primary .btn-action .btn .btn-success .btn-lg role="button" target="_blank" data-tippy-content="Register for the virtual event (free)"}

[Expo Submission](https://docs.google.com/forms/d/e/1FAIpQLSeTxjipa92YWmM6ZZhb2C6hFKmlB2b7eYaQ33lQZIIu-wuOPw/viewform?usp=sharing&ouid=116517077506150901012){.btn-action-primary .btn-action .btn .btn-success .btn-lg role="button" target="_blank" data-tippy-content="Submit a booth for the genAI Expo session"}
::::

The third Annual R/Pharma genAI Day will be held virtually on **June 16, 2026**.  This free single day event will focus on examples of using generative and agentic artificial intelligence with an emphasis in the drug development space and clinical domain.

This page contains details and a schedule for the event.  For registration and other information, please visit [R/Pharma genAI Day](https://events.zoom.us/ev/AkKYQ7Uryr8k8HeuQ7F6rkZTHJwjHlP6gxu14Z2s1LYb0kswLdDT~ApU4J3CViJWrwmjZhnw0nwGzDFCxNGoMHJAw01NbG30yNwnVwf9IJQkvOg){target="_blank"}.

## Calling all Open Source Developers!

We will be featuring a virtual exhibition hall that will be open throughout the event.  This is a chance for you to showcase your awesome open source creations!  Please consider sharing your work in a virtual booth if you:

- have an R or Python package or app
- have created a useful AI agent or skill
- contribute to the community through a YouTube channel, blog or podcast

If you wish to include a virtual booth please use contribute using the [EXPO Form](https://docs.google.com/forms/d/e/1FAIpQLSeTxjipa92YWmM6ZZhb2C6hFKmlB2b7eYaQ33lQZIIu-wuOPw/viewform?usp=sharing&ouid=116517077506150901012){target="_blank"}.

## Schedule

Tap or hover on talk titles for abstracts and speaker names for bios.  All times are in EDT.

```{r}
#| echo: FALSE
#| warning: FALSE
library(yaml)
library(purrr)
library(tibble)
library(htmltools)

file <- "./schedule.yml"

raw <- yaml::read_yaml(file)

normalize_speakers <- function(s) {
  if (is.null(s)) return(NULL)
  lapply(s, function(x) {
    list(
      name = x$name,
      affiliation = if (!is.null(x$affiliation) && nzchar(x$affiliation)) x$affiliation else NULL,
      bio = x$bio %||% ""
    )
  })
}

schedule <- tibble(
  time = map_chr(raw, "time"),
  type = map_chr(raw, "type"),
  title = map_chr(raw, "title"),
  duration = map_chr(raw, "duration"),
  abstract = map_chr(raw, ~ .x$abstract %||% ""),
  speakers = map(raw, ~ normalize_speakers(.x$speakers))
)

speaker_tag <- function(name, affiliation, bio) {

  has_text <- function(x) {
    !is.null(x) && length(x) == 1 && !is.na(x) && nzchar(x)
  }

  label <- name
  if (has_text(affiliation)) {
    label <- paste0(name, " (", affiliation, ")")
  }

  if (has_text(bio)) {
    tags$span(
      class = "has-tooltip speaker",
      `data-tippy-content` = paste0(
        "<strong>", name, "</strong>",
        if (has_text(affiliation)) {
          paste0("<br><em>", affiliation, "</em>")
        } else "",
        "<br><br>", bio
      ),
      HTML(label)
    )
  } else {
    tags$span(class = "speaker", label)
  }
}

speakers_block <- function(speakers) {

  if (is.null(speakers) || length(speakers) == 0) return(NULL)

  # 🔑 unwrap common YAML/list-column nesting issue
  if (length(speakers) == 1 && is.list(speakers[[1]]) && !is.null(speakers[[1]][[1]]$name)) {
    speakers <- speakers[[1]]
  }

  tagList(
    purrr::imap(speakers, function(sp, i) {
      tagList(
        speaker_tag(
          sp$name %||% "",
          sp$affiliation %||% "",
          sp$bio %||% NULL
        ),
        if (i < length(speakers)) ", "
      )
    })
  )
}

title_tag <- function(title, abstract) {

  has_text <- function(x) {
    !is.null(x) && length(x) == 1 && !is.na(x) && nzchar(x)
  }

  if (has_text(abstract)) {
    tags$span(
      class = "has-tooltip talk-title",
      `data-tippy-content` = paste0(
        "<strong>Abstract</strong><br><br>", abstract
      ),
      title
    )
  } else {
    tags$span(class = "talk-title", title)
  }
}

render_row <- function(row) {

  if (row$type == "break") {
    return(
      tags$div(class = "schedule-row break",
        tags$div(class = "time", row$time),
        tags$div(class = "content",
          tags$strong(row$title),
          tags$span(class = "duration", row$duration)
        )
      )
    )
  }

  tags$div(class = "schedule-row talk",
    tags$div(class = "time", row$time),
    tags$div(class = "content",

      speakers_block(row$speakers),

      if (!is.null(row$speakers) && length(row$speakers) > 0) tags$br(),

      tags$div(class = "title-row",
        title_tag(row$title, row$abstract),
        tags$span(class = "duration", row$duration)
      )
    )
  )
}

schedule_html <- tags$div(class = "schedule-container",
  tagList(
    lapply(seq_len(nrow(schedule)), function(i) {
      render_row(schedule[i, ])
    })
  )
)
```

```{r}
#| echo: FALSE
#| output: asis
schedule_html
```
